cardinalR: Generating interesting high-dimensional data structures

### 2025-09-19 paper-cardinalR.tex
Need to add a section for All noise in one
Updated mobius section with general noise dimensions

The Mobius strip is generated using the \texttt{geozoo::mobius} function with \texttt{p\ =\ 3}, and \texttt{n} defined as above. Each point is sampled from a parameterization defined by an angle \(\theta \sim U(0, 2\pi)\), which specifies the position along the circular loop, and a width \(w \sim U(-0.4, 0.4)\), which offsets the point across the strip's band. The cartesian coordinates are \(X_1 = \left(1 + (w/2) \cos(\theta/2)\right) \cos(\theta)\), \(X_2 = \left(1 + (w/2) \cos(\theta/2)\right) \sin(\theta)\), and \(X_3 = (w/2)\sin(\theta/2)\). This maps a \(2\text{-}D\) band with a half-twist into \(3\text{-}D\) space, forming a non-orientable one-sided surface. For \(p > 3\), Gaussian noise \(X_j \sim N(0, 0.05^2)\) is added to embed the \(3\text{-}D\) Mobius into \(p\text{-}D\), where \(j = 4, \dots, p\).

@@

>>>>

The Mobius strip is generated using the \texttt{geozoo::mobius} function with \texttt{p\ =\ 3}, and \texttt{n} defined as above. Each point is sampled from a parameterization defined by an angle \(\theta \sim U(0, 2\pi)\), which specifies the position along the circular loop, and a width \(w \sim U(-0.4, 0.4)\), which offsets the point across the strip's band. The cartesian coordinates are \(X_1 = \left(1 + (w/2) \cos(\theta/2)\right) \cos(\theta)\), \(X_2 = \left(1 + (w/2) \cos(\theta/2)\right) \sin(\theta)\), and \(X_3 = (w/2)\sin(\theta/2)\). This maps a \(2\text{-}D\) band with a half-twist into \(3\text{-}D\) space, forming a non-orientable one-sided surface. For \(p > 3\), additional noise dimension are added to embed the \(3\text{-}D\) Mobius into \(p\text{-}D\).

@@

\subsubsection{Generate noise dimensions}\label{generate-noise-dimensions}
